---
title: "Genome lengths"
output:
  html_document:
    df_print: paged
---

# plot the distribution of plant genome lengths
A table of plant genomes and their respective lengths was acquired from [NCBI Entrez](https://www.ncbi.nlm.nih.gov/genome/browse/#!/overview/plants). Here I import it in R.

```{r}
#install.packages("data.table")
library(data.table)
ncbi_lengths <- fread(file = "./genome_lengths.csv",sep = ',',header = T)
head(ncbi_lengths)
```

I notice that one genome has a length of 0, perhaps this will be updated in the near future. 
```{r}
ncbi_lengths[ncbi_lengths[,which(ncbi_lengths[,3] ==0)]]
```

Let's take it out for now
```{r}
ncbi_lengths <- ncbi_lengths[Size_Mb>0]
```


Now let's have a look at the distribution of genome lengths
```{r}
#install.packages("ggplot2")
library(ggplot2)
plot_length_dist <- ggplot(data = ncbi_lengths,mapping = aes(x=Size_Mb))
plot_length_dist <- plot_length_dist + geom_histogram(fill='blue',binwidth = 100)
plot_length_dist <- plot_length_dist + theme_classic()
#plot_length_dist <- plot_length_dist + scale_x_continuous(trans = 'log10')
plot_length_dist
```

not very intuitive, let's log transform


```{r}
#install.packages("ggplot2")
#library(ggplot2)
plot_length_dist <- ggplot(data = ncbi_lengths,mapping = aes(x=Size_Mb))
plot_length_dist <- plot_length_dist + geom_histogram(fill='blue',binwidth = 0.1)
plot_length_dist <- plot_length_dist + theme_classic()
plot_length_dist <- plot_length_dist + scale_x_continuous(trans = 'log2')
plot_length_dist
```

Funny, I had expected that peak to be a lot lower. I doubt there is genomes for all these species but that is for another time.

What I really need next is to have assemblies+accession numbers -> FastQ data in a systematic way in the same sheet.
Then most importantly, I'll need the rRNA copy numbers, ideally also in some organised fashion. 
